---
title: "MyMark"
author: "AlketCecaj"
date: "09 gennaio 2017"
output: html_document
---

##Loading data
```{r, echo = FALSE}
setwd("C:/Users/alketcecaj/Documents/traindelays");
r2b <- read.csv("C:/Users/alketcecaj/Documents/traindelays/BolognaDelays.csv", sep = "\t", T )
b2r <- read.csv("C:/Users/alketcecaj/Documents/traindelays/ReggioDelays.csv", sep = "\t", T )
head(r2b)
```
<span style="color:red; font-family:Georgia; font-size:2em;">All the delays are expressed in minutes</span>

###Delay distribution during the observed period

```{r histogram, echo = FALSE}

hist(r2b$Ritardo_In_Minuti,main = "Dealys Reggio Emilia - Bologna", xlab="Delay", breaks = 20)
hist(b2r$Ritardo_In_Minuti,main = "Delays Bologna - Reggio Emilia",  xlab="Delay",breaks = 20)
```

### Accumulated Delay per day Bologna

```{r, echo = FALSE}
setwd("C:/Users/alketcecaj/Documents");
delayT_r2b <- read.csv("C:/Users/alketcecaj/Documents/traindelays/Delay2Train_BolognaDelays.csv", sep = "\t", T )
delayT_b2r <- read.csv("C:/Users/alketcecaj/Documents/traindelays/Delay2Train_ReggioDelays.csv", sep = "\t", T )

delayD_r2b <- read.csv("C:/Users/alketcecaj/Documents/traindelays/Delay2Day_BolognaDelays.csv", sep = "\t", T )
delayD_b2r <- read.csv("C:/Users/alketcecaj/Documents/traindelays/Delay2Day_ReggioDelays.csv", sep = "\t", T )

barplot(delayD_r2b$Ritardo,  names.arg= delayD_r2b$Giorno, cex.names=0.8,col="blue", las=2)

```

### Accumulated Delay per train Bologna

```{r, echo = FALSE}
barplot(delayT_r2b$Ritardo,  names.arg= delayT_r2b$Nr_Treno, cex.names=0.8,col="blue", las = 2)

```

### Accumulated Delay per day Reggio Emilia

```{r, echo = FALSE}
barplot(delayD_b2r$Ritardo,  names.arg= delayD_b2r$Giorno, col="red", cex.names=0.8,las = 2)

```

### Accumulated Delay per train Reggio Emilia

```{r, echo = FALSE}
barplot(delayT_b2r$Ritardo,  names.arg= delayT_b2r$Nr_Treno, cex.names=0.8,col="red", las = 2)

```

### Accumulated Delay per weekday Bologna

```{r, echo = FALSE}
setwd("C:\\Users\\alketcecaj\\Documents");
delayWD_b <- read.csv("C:/Users/alketcecaj/Documents/traindelays/Delay2WeekDay_BolognaDelays.csv", sep = "\t", T )
delayWD_r <- read.csv("C:/Users/alketcecaj/Documents/traindelays/Delay2WeekDay_ReggioDelays.csv", sep = "\t", T )

barplot(delayWD_b$Ritardo,  names.arg= delayWD_b$Giorno, col="blue")

```

### Accumulated Delay per weekday Reggio Emilia

```{r, echo = FALSE}
barplot(delayWD_r$Ritardo,  names.arg= delayWD_r$Giorno, col="red")

```

### Accumulated Delay upon arrival at Bologna per hour

```{r, echo = FALSE}
setwd("C:\\Users\\alketcecaj\\Documents");
delayH_b <- read.csv("C:/Users/alketcecaj/Documents/traindelays/DelayPerHour_BolognaDelays.csv", sep = "\t", T )
delayH_r <- read.csv("C:/Users/alketcecaj/Documents/traindelays/DelayPerHour_ReggioDelays.csv", sep = "\t", T )

barplot(delayH_b$Ritardo,  names.arg= delayH_b$Ora, col="blue")

```

### Accumulated Delay upon arrival at Reggio Emilia station per hour

```{r, echo = FALSE}
barplot(delayH_r$Ritardo,  names.arg= delayH_r$Ora, col="red")

```